% \documentclass[preprint,12pt,authoryear]{elsarticle}
% \input{instr-preamble}
% \input{instr-mathsymbols}
% \journal{ME517---Mechanics of Soft Materials}
% \setlength{\marginparwidth}{2cm}
% \newcommand\C[1]\null %\C{for inline comments}
% \begin{document}

% \include{instr-part2}
% \include{Dawson-part1}

\section{Introductory context}
\begin{itemize}
    \item Microtubules are intracellular filaments composed of tubulin subunits [\cite{rev_nogales}]. As the most rigid cytoskeletal filament [\cite{rev_mechanics}], microtubules serve multiple mechanical roles in cells including maintenance of cell shape [\cite{rev_org-shape}], generation of intracellular forces [\cite{rev_push-pull}], and cell migration [\cite{rev_migration}]. Despite their relative rigidity, microtubules can bend under intracellular forces [\cite{p_bend-in-cells}]. This bending is functionally important in platelets [\cite{rev_platelet-MTs}] and cardiomyocytes [\cite{rev_carmy-MTs}].
    \item Measurements of microtubule mechanical properties have focused on their flexural rigidity [\cite{p_thermal-flex}], and experimental papers generally model microtubules as thin elastic beams [\cite{rev_mechanics}]. However, measurements of microtubule mechanics over the past couple of decades are and have remained highly variable [\cite{rev_hawkins}]. More recent work has tried to address these discrepancies by investigating different factors that could impact mechanics, including polymerization rate [\cite{p_growth-rate-1, p_growth-rate-2}], temperature [\cite{p_temp}], salt concentration [\cite{p_salt}], presence of stabilizing agents [\cite{p_stabilize}], and microtubule length [\cite{p_length-1}]. Other papers have noted behaviors that contradict with the view of microtubules as purely elastic materials, including strain-dependent responses [\cite{p_strain-soften}] and increased deformation with repeated bending [\cite{p_repeated-flow}].
\end{itemize}

\section{The state of the field}
\begin{itemize}
    \item The most common experimental methods to measure microtubule mechanics are thermal fluctuations [\cite{p_thermal-flex, p_therm-flex-2}], hydrodynamic flow [\cite{p_flow-1}], and optical trapping [\cite{p_trap-1, p_trap-2}].
    \item Although microtubules are often treated as elastic beams in experimental papers [\cite{rev_mechanics}], other models of microtubule behaviors have been published. Current models of microtubule bending include (1) molecular dynamics or other atomic models [\cite{p_Molec-Dyn-1, p_atomic-1}], (2) models noting the interactions of the thinner protofilaments composing microtubules [\cite{p_protofil-1, p_protofil-2}], and (3) continuum models focusing on the anisotropic elastic properties of microtubules [\cite{p_aniso-2, p_aniso-3, p_aniso-4}]. Viscoelastic models of microtubules have generally been restricted to microtubule networks [\cite{rev_visco, p_visco-network}], models considering the viscous properties of the surrounding cytosol [\cite{p_visco-cytosol}], or models looking at cell-type specific configurations of microtubule bundles [\cite{p_visco-bundle, p_visco-myocyte}]. At least one paper proposed a viscoelastic model for microtubule bending, although without specific paired experiments [\cite{p_visco-model}].
\end{itemize}

\section{The Big Gap}
\begin{itemize}
    \item As far as I am aware, it remains to be directly experimentally tested whether single microtubules demonstrate elastic or viscoelastic behaviors.
    \item The most challenging barrier to doing these experiments seems to be the availability of techniques for making such measurements.
    \item As a note, I'm slightly less sure that my proposed project will be novel given what I found in the literature so far. It seems quite possible that, with a little more looking, I could find that it has already been done. Any suggestions on how to push the project a little farther to address this would be greatly appreciated!
    % \item I should note, the more papers I find the more I am wondering if this *has* been addressed already. 
\end{itemize}

% While a few viscoelastic models have been proposed and aspects of multiple experiments suggest the potential for microtubules to be viscoelastic, 

\begin{thebibliography}{00} % using Chicago 18th shortened from Zotero

\bibitem[Nogales, 2025]{rev_nogales}
Nogales, Eva. Structural Insights into Microtubule Function. 2025. % review, general microtubules. Roles in cell shape, transport, motility, division.

\bibitem[Romet-Lemonne et al., 2025]{rev_mechanics}
Romet-Lemonne, Guillaume, Cécile Leduc, Antoine Jégou, and Hugo Wioland. “Mechanics of Single Cytoskeletal Filaments.” Annual Review of Biophysics 54, no. 1 (2025): 303–27. https://doi.org/10.1146/annurev-biophys-030722-120914. % review, mechanics of microtubules (focus on mechanical properties rather than functional roles of microtubule mechanics)

\bibitem[Akhmanova and Kapitein, 2022]{rev_org-shape}
Akhmanova, Anna, and Lukas C. Kapitein. “Mechanisms of Microtubule Organization in Differentiated Animal Cells.” Nature Reviews Molecular Cell Biology 23, no. 8 (2022): 541–58. https://doi.org/10.1038/s41580-022-00473-y.

\bibitem[Gudimchuk et al., 2023]{rev_push-pull}
Gudimchuk, Nikita B., and Veronika V. Alexandrova. “Measuring and Modeling Forces Generated by Microtubules.” Biophysical Reviews 15, no. 5 (2023): 1095–110. https://doi.org/10.1007/s12551-023-01161-7. % review, force generation by microtubules

\bibitem[Schmidt and Stehbens, 2024]{rev_migration}
Schmidt, Christanny J., and Samantha J. Stehbens. “Microtubule Control of Migration: Coordination in Confinement.” Current Opinion in Cell Biology 86 (February 2024): 102289. https://doi.org/10.1016/j.ceb.2023.102289. % review

\bibitem[Pallavicini et al., 2014]{p_bend-in-cells}
Pallavicini, Carla, Valeria Levi, Diana E. Wetzler, et al. “Lateral Motion and Bending of Microtubules Studied with a New Single-Filament Tracking Routine in Living Cells.” Biophysical Journal 106, no. 12 (2014): 2625–35. https://doi.org/10.1016/j.bpj.2014.04.046. % primary

\bibitem[Sadoul, 2015]{rev_platelet-MTs}
Sadoul, K. “New Explanations for Old Observations: Marginal Band Coiling during Platelet Activation.” Journal of Thrombosis and Haemostasis 13, no. 3 (2015): 333–46. https://doi.org/10.1111/jth.12819. % review, microtubules in platelet shape

\bibitem[Uchida et al., 2022]{rev_carmy-MTs}
Uchida, Keita, Emily A. Scarborough, and Benjamin L. Prosser. “Cardiomyocyte Microtubules: Control of Mechanics, Transport, and Remodeling.” Annual Review of Physiology 84, no. Volume 84, 2022 (2022): 257–83. https://doi.org/10.1146/annurev-physiol-062421-040656. % review, microtubules in cardiomyocyte contractility

\bibitem[Gittes et al., 1993]{p_thermal-flex}
Gittes, F, B Mickey, J Nettleton, and J Howard. “Flexural Rigidity of Microtubules and Actin Filaments Measured from Thermal Fluctuations in Shape.” Journal of Cell Biology 120, no. 4 (1993): 923–34. https://doi.org/10.1083/jcb.120.4.923.

\bibitem[Hawkins et al., 2010]{rev_hawkins}
Hawkins, Taviare, Matthew Mirigian, M. Selcuk Yasar, and Jennifer L. Ross. “Mechanics of Microtubules.” Journal of Biomechanics 43, no. 1 (2010): 23–30. https://doi.org/10.1016/j.jbiomech.2009.09.005. % review, differences in measurements of mechanical properties

\bibitem[Zhou et al., 2021]{p_growth-rate-1}
Zhou, Hang, Naoto Isozaki, Kazuya Fujimoto, and Ryuji Yokokawa. “Growth Rate-Dependent Flexural Rigidity of Microtubules Influences Pattern Formation in Collective Motion.” Journal of Nanobiotechnology 19, no. 1 (2021): 218. https://doi.org/10.1186/s12951-021-00960-y.

\bibitem[Janson and Dogterom, 2004]{p_growth-rate-2}
Janson, Marcel E., and Marileen Dogterom. “A Bending Mode Analysis for Growing Microtubules: Evidence for a Velocity-Dependent Rigidity.” Biophysical Journal 87, no. 4 (2004): 2723–36. https://doi.org/10.1529/biophysj.103.038877.

\bibitem[Kawaguchi et al., 2008]{p_temp}
Kawaguchi, Kenji, Shin’ichi Ishiwata, and Toshihide Yamashita. “Temperature Dependence of the Flexural Rigidity of Single Microtubules.” Biochemical and Biophysical Research Communications 366, no. 3 (2008): 637–42. https://doi.org/10.1016/j.bbrc.2007.11.162.

\bibitem[Harris et al., 2018]{p_salt}
Harris, Brandon J., Jennifer L. Ross, and Taviare L. Hawkins. “Microtubule Seams Are Not Mechanically Weak Defects.” Physical Review E 97, no. 6 (2018): 062408. https://doi.org/10.1103/PhysRevE.97.062408.

\bibitem[Mickey and Howard, 1995]{p_stabilize}
Mickey, B., and J. Howard. “Rigidity of Microtubules Is Increased by Stabilizing Agents.” The Journal of Cell Biology 130, no. 4 (1995): 909–17. https://doi.org/10.1083/jcb.130.4.909.

\bibitem[Pampaloni et al., 2006]{p_length-1}
Pampaloni, Francesco, Gianluca Lattanzi, Alexandr Jonáš, Thomas Surrey, Erwin Frey, and Ernst-Ludwig Florin. “Thermal Fluctuations of Grafted Microtubules Provide Evidence of a Length-Dependent Persistence Length.” Proceedings of the National Academy of Sciences 103, no. 27 (2006): 10248–53. https://doi.org/10.1073/pnas.0603931103. % primary, length dependent persistence length

\bibitem[Memet et al., 2018]{p_strain-soften}
Memet, Edvin, Feodor Hilitski, Margaret A Morris, Walter J Schwenger, Zvonimir Dogic, and L Mahadevan. “Microtubules Soften Due to Cross-Sectional Flattening.” eLife 7 (June 2018): e34695. https://doi.org/10.7554/eLife.34695. % softening at high strains? is the critical strain biologically relavent?

\bibitem[Portran et al., 2017]{p_repeated-flow}
Portran, Didier, Laura Schaedel, Zhenjie Xu, Manuel Théry, and Maxence V. Nachury. “Tubulin Acetylation Protects Long-Lived Microtubules against Mechanical Ageing.” Nature Cell Biology 19, no. 4 (2017): 391–98. https://doi.org/10.1038/ncb3481. % primary, acetylation as a tubulin PTM impacts mechanical properties AND change in bending with repeated flow cycles

\bibitem[Valdman et al., 2012]{p_therm-flex-2}
Valdman, David, Paul J. Atzberger, Dezhi Yu, Steve Kuei, and Megan T. Valentine. “Spectral Analysis Methods for the Robust Measurement of the Flexural Rigidity of Biopolymers.” Biophysical Journal 102, no. 5 (2012): 1144–53. https://doi.org/10.1016/j.bpj.2012.01.045.

\bibitem[Venier et al., 1994]{p_flow-1}
Venier, P., A.C. Maggs, M.F. Carlier, and D. Pantaloni. “Analysis of Microtubule Rigidity Using Hydrodynamic Flow and Thermal Fluctuations.” Journal of Biological Chemistry 269, no. 18 (1994): 13353–60. https://doi.org/10.1016/S0021-9258(17)36840-0.

\bibitem[Kurachi et al., 1995]{p_trap-1}
Kurachi, Masashi, Masayuki Hoshi, and Hideo Tashiro. “Buckling of a Single Microtubule by Optical Trapping Forces: Direct Measurement of Microtubule Rigidity.” Cell Motility 30, no. 3 (1995): 221–28. https://doi.org/10.1002/cm.970300306.

\bibitem[van Mameren et al., 2009]{p_trap-2}
van Mameren, Joost van, Karen C. Vermeulen, Fred Gittes, and Christoph F. Schmidt. “Leveraging Single Protein Polymers To Measure Flexural Rigidity.” The Journal of Physical Chemistry B 113, no. 12 (2009): 3837–44. https://doi.org/10.1021/jp808328a.

\bibitem[Septh and MacKintosh, 2010]{p_Molec-Dyn-1}
Sept, David, and Fred C. MacKintosh. “Microtubule Elasticity: Connecting All-Atom Simulations with Continuum Mechanics.” Physical Review Letters 104, no. 1 (2010): 018101. https://doi.org/10.1103/PhysRevLett.104.018101.

\bibitem[Molodtsov et al., 2005]{p_atomic-1}
Molodtsov, Maxim I., Elena A. Ermakova, Emmanuil E. Shnol, Ekaterina L. Grishchuk, J. Richard McIntosh, and Fazly I. Ataullakhanov. “A Molecular-Mechanical Model of the Microtubule.” Biophysical Journal 88, no. 5 (2005): 3167–79. https://doi.org/10.1529/biophysj.104.051789.

% \bibitem[Li et al., 2006]{p_aniso-1}
% Li, C., C.Q. Ru, and A. Mioduchowski. “Length-Dependence of Flexural Rigidity as a Result of Anisotropic Elastic Properties of Microtubules.” Biochemical and Biophysical Research Communications 349, no. 3 (2006): 1145–50. https://doi.org/10.1016/j.bbrc.2006.08.153. % primary, reported difference sin flexural rigidity due to inaccuracy of isotropic beam model for shorter microtubule lengths, and that longitudinal (rather than circumferential) Young's modulus is length-independent due to anisotropic elastic properties of microtubules

\bibitem[Wang et al., 2006]{p_aniso-2}
Wang, C.Y., C.Q. Ru, and A. Mioduchowski. “Orthotropic Elastic Shell Model for Buckling of Microtubules.” Physical Review E 74, no. 5 (2006): 052901. https://doi.org/10.1103/PhysRevE.74.052901. % primary, anisotropic elastic shell model rather than isotropic elastic shell model (similar to other paper)

\bibitem[Liew et al., 2011]{p_aniso-3}
Liew, K.M., Ping Xiang, and Yuzhou Sun. “A Continuum Mechanics Framework and a Constitutive Model for Predicting the Orthotropic Elastic Properties of Microtubules.” Composite Structures 93, no. 7 (2011): 1809–18. https://doi.org/10.1016/j.compstruct.2011.01.017. % primary

\bibitem[Deriu et al., 2010]{p_aniso-4}
Deriu, Marco A., Monica Soncini, Mario Orsi, et al. “Anisotropic Elastic Network Modeling of Entire Microtubules.” Biophysical Journal 99, no. 7 (2010): 2190–99. https://doi.org/10.1016/j.bpj.2010.06.070.

\bibitem[Wang et al., 2016]{p_protofil-1}
Wang, Chengyuan, Zhigang Guo, Ruijie Wang, and Ying Luo. “Role of the Inter-Protofilament Sliding in the Bending of Protein Microtubules.” Journal of Biomechanics 49, no. 16 (2016): 3803–7. https://doi.org/10.1016/j.jbiomech.2016.10.008.

\bibitem[Ye et al., 2025]{p_protofil-2}
Ye, Yucheng, Zheng Hao, Jingyi Luo, et al. “Tubulin Isotypes of C. Elegans Harness the Mechanosensitivity of the Lattice for Microtubule Luminal Accessibility.” Nature Physics, ahead of print, August 26, 2025. https://doi.org/10.1038/s41567-025-02983-w.

\bibitem[Liew et al., 2015]{rev_models}
Liew, K.M., Ping Xiang, and L.W. Zhang. “Mechanical Properties and Characteristics of Microtubules: A Review.” Composite Structures 123 (May 2015): 98–108. https://doi.org/10.1016/j.compstruct.2014.12.020. % review

\bibitem[Corominas-Murtra and Petridou, 2021]{rev_visco}
Corominas-Murtra, Bernat, and Nicoletta I. Petridou. “Viscoelastic Networks: Forming Cells and Tissues.” Frontiers in Physics 9 (2021). https://doi.org/10.3389/fphy.2021.666916. % review, actin and vimentin at single filament level show nonlinear increase in shear modulus at different strain amplitudes, an dmore appaent at network level with crosslinks influencing viscoelastic behavior of network. Transient and non-covalent crosslinking interactions to form viscoelastic material whereas covalent an elastic material. **NOT READ**

\bibitem[Lin et al., 2007]{p_visco-network}
Lin, Yi-Chia, Gijsje H. Koenderink, Frederick C. MacKintosh, and David A. Weitz. “Viscoelastic Properties of Microtubule Networks.” Macromolecules 40, no. 21 (2007): 7714–20. https://doi.org/10.1021/ma070862l. % primary, linear viscoelastic properties of microtubule networks

\bibitem[Li, 2008]{p_visco-cytosol}
Li, Teng. “A Mechanics Model of Microtubule Buckling in Living Cells.” Journal of Biomechanics 41, no. 8 (2008): 1722–29. https://doi.org/10.1016/j.jbiomech.2008.03.003.

\bibitem[Shamloo et al., 2015]{p_visco-bundle}
Shamloo, Amir, Farid Manuchehrfar, and Hashem Rafii-Tabar. “A Viscoelastic Model for Axonal Microtubule Rupture.” Journal of Biomechanics 48, no. 7 (2015): 1241–47. https://doi.org/10.1016/j.jbiomech.2015.03.007.

\bibitem[Caporizzo et al., 2018]{p_visco-myocyte}
Caporizzo, Matthew Alexander, Christina Yingxian Chen, Alexander Koizumi Salomon, Kenneth B. Margulies, and Benjamin L. Prosser. “Microtubules Provide a Viscoelastic Resistance to Myocyte Motion.” Biophysical Journal 115, no. 9 (2018): 1796–807. https://doi.org/10.1016/j.bpj.2018.09.019.

\bibitem[Abdelmalek et al., 2021]{p_visco-model}
Abdelmalek, Zahra, Mohammed Karbon, Arameh Eyvazian, Ali Forooghi, Hamed Safarpour, and Iskander Tlili. “On the Dynamics of a Curved Microtubule-Associated Proteins by Considering Viscoelastic Properties of the Living Biological Cells.” Journal of Biomolecular Structure and Dynamics 39, no. 7 (2021): 2415–29. https://doi.org/10.1080/07391102.2020.1747549.


\bibliographystyle{elsarticle-harv} 
% \bibliography{cas-refs}
\end{thebibliography}

% \end{document}


% do they compress with bending?
% Functional roles are based on proteins and motors bound to microtubules [ ] as well as the in
    
    % include transport in cells [\cite{rev_transport}], cell migration [/cite{rev_migration}], maintenance of cell shape, cell division, and more. While some of these roles result from other proteins or motors bound to microtubules.

%     Microtubules are dynamic intracellular filaments composed of tubulin subunits [\cite{rev_nogales}]. As the most rigid cytoskeleton filament [], a primary cellular role is as pathways for intracellular transport []. However, microtubules also have multiple mechanical roles in cells, including maintenance of cell shape [multiple], generation of pushing and pulling forces [], and providing compressive resistance to bending []. Despite their relative rigidity, microtubules are also bendable under intracellular forces [bending in cells]. This ability to bend serves functional roles in platelets [] and cardiomyocytes [].  %Microtubules in cells perform functional roles as cross-linked networks [], filamentous bundles [], and other configurations [].

% %    
    
%     \item While some mechanical functions are based on cross-linked networks of microtubules [], many microtubules work individually or in small groups [Hawkins plus others, do find those citations though]. The lack of need to cross link based in stiffness according to Gittes [Gittes for history]. Microtubules also not extendable and filaments either bend or slide between each other rather than induvidually stretch [also gittes]. More recent measurements acknowledge something beyond elastic beams. Emerging work trying to address to discrepencies in measurements by looking at different factors could depend on. [Zhou, growth rate]

    %    The mechanical properties of single microtubules are most commonly measured through optical trapping [], hydrodynamic flow [], or thermal fluctuations []. Current measurements of bending modulus are highly variable []. Experimental papers will commonly characterize microtubule bending as that of an isotropic elastic rod [multiple]. This inconsistency, along with studies noting the potential for anisotropic behaviors [] and smaller-scale mechanical interactions [], suggest a requirement for more comprehensive physical models of their mechanical behavior. [Memet cross sectional flattening, deviate from simple elastic model with softening response captured by flattening, ALSO strain magnitude dependence] [so some folks have already looked...wasn't there one for cardiomyocytes that had a VE regime, was that for single or bundles]




% %%%% Additions
% \bibitem[Ye et al., 2025]{p_lumen}
% Ye, Yucheng, Zheng Hao, Jingyi Luo, et al. “Tubulin Isotypes of C. Elegans Harness the Mechanosensitivity of the Lattice for Microtubule Luminal Accessibility.” Nature Physics, ahead of print (2025). https://doi.org/10.1038/s41567-025-02983-w. % primary, tubulin isotypes and mechanics as well as protofilament interactions during bending for different isotypes
% Nishida, Kohei, Kosuke Matsumura, Miki Tamura, et al. “Effects of Three Microtubule-Associated Proteins (MAP2, MAP4, and Tau) on Microtubules’ Physical Properties and Neurite Morphology.” Scientific Reports 13, no. 1 (2023): 8870. https://doi.org/10.1038/s41598-023-36073-9.
% \bibitem[]{}
% Xu, Zhenjie, Laura Schaedel, Didier Portran, et al. “Microtubules Acquire Resistance from Mechanical Breakage through Intralumenal Acetylation.” Science 356, no. 6335 (2017): 328–32. https://doi.org/10.1126/science.aai8764. % primary, acetylation as a tubulin PTM impacts mechanical properties
% \bibitem[]{}
% Xu, Zhenjie, Laura Schaedel, Didier Portran, et al. “Microtubules Acquire Resistance from Mechanical Breakage through Intralumenal Acetylation.” Science 356, no. 6335 (2017): 328–32. https://doi.org/10.1126/science.aai8764.
% \bibitem[]{}
% Mehrbod, Mehrdad, and Mohammad R. K. Mofrad. “On the Significance of Microtubule Flexural Behavior in Cytoskeletal Mechanics.” PLOS ONE 6, no. 10 (2011): e25627. https://doi.org/10.1371/journal.pone.0025627. % buckling modes?

% %%% Microtubules in general
% \bibitem[Agrawal et al., 2022]{rev_transport}
% Agrawal, Anamika, Zubenelgenubi C. Scott, and Elena F. Koslover. “Morphology and Transport in Eukaryotic Cells.” Annual Review of Biophysics 51, no. Volume 51, 2022 (2022): 247–66. https://doi.org/10.1146/annurev-biophys-111121-103956. % review, transport in cells
% \bibitem[]{}
% Sulerud, Taylor, Abdullah Bashar Sami, Guihe Li, April Kloxin, John Oakey, and Jesse Gatlin. “Microtubule-Dependent Pushing Forces Contribute to Long-Distance Aster Movement and Centration in Xenopus Laevis Egg Extracts.” Molecular Biology of the Cell 31, no. 25 (2020): 2791–802. https://doi.org/10.1091/mbc.E20-01-0088. % primary, cell division centering based on microtubule based pushing mechanisms
% \bibitem[]{}
% Rodionov, V I, F K Gyoeva, E Tanaka, A D Bershadsky, J M Vasiliev, and V I Gelfand. “Microtubule-Dependent Control of Cell Shape and Pseudopodial Activity Is Inhibited by the Antibody to Kinesin Motor Domain.” The Journal of Cell Biology 123, no. 6 (1993): 1811–20. https://doi.org/10.1083/jcb.123.6.1811. % primary, cell shape also requires motors
% \bibitem[Behnke]{p_platelet-MB}
% Behnke, O. “A Comparative Study of Microtubules of Disk-Shaped Blood Cells.” Journal of Ultrastructure Research 31, nos. 1–2 (1970): 61–75. https://doi.org/10.1016/S0022-5320(70)90145-0. % primary, marginal band required for cell shape in SOME cell types, including platelets
% \bibitem[]{p_platelet-shape}
% Italiano, Joseph E., Jr, Wolfgang Bergmeier, Sanjay Tiwari, et al. “Mechanisms and Implications of Platelet Discoid Shape.” Blood 101, no. 12 (2003): 4789–96. https://doi.org/10.1182/blood-2002-11-3491. % primary

% %%% Tubulin Code
% \bibitem[]{}
% Janke, Carsten, and Maria M. Magiera. “The Tubulin Code and Its Role in Controlling Microtubule Properties and Functions.” Nature Reviews Molecular Cell Biology 21, no. 6 (2020): 307–26. https://doi.org/10.1038/s41580-020-0214-3. % review, overall tubulin code
% \bibitem[]{}
% Gasic, Ivana. “Regulation of Tubulin Gene Expression: From Isotype Identity to Functional Specialization.” Frontiers in Cell and Developmental Biology 10 (May 2022). https://doi.org/10.3389/fcell.2022.898076. % review, functional specialization from different isotypes **NOT READ**
% \bibitem[]{}
% Janke, Carsten, and Jeannette Chloë Bulinski. “Post-Translational Regulation of the Microtubule Cytoskeleton: Mechanisms and Functions.” Nature Reviews Molecular Cell Biology 12, no. 12 (2011): 773–86. https://doi.org/10.1038/nrm3227. % review, functional specialization from different PTMS **NOT READ**

% %%% Mechanical Properties

% %%% Mechanical Roles
% \bibitem[]{}
% Matis, Maja. “The Mechanical Role of Microtubules in Tissue Remodeling.” BioEssays 42, no. 5 (2020): 1900244. https://doi.org/10.1002/bies.201900244. % review, microtubules in cellular trafficking and signaling during tissue formation as well as direct mechanical roles **NOT READ**

% \bibitem[]{}
% Garcin, Clare, and Anne Straube. “Microtubules in Cell Migration.” Essays in Biochemistry 63, no. 5 (2019): 509–20. https://doi.org/10.1042/EBC20190016. % review, microtubule roles in directed cell migration (as tracks for intracellular transport, force generation, compressive elements to support protrusions, and signaling) **NOT READ**

% %%% Health examples
% \bibitem[Caporizzo and Prosser, 2022]{card_HF}
% Caporizzo, Matthew A., and Benjamin L. Prosser. “The Microtubule Cytoskeleton in Cardiac Mechanics and Heart Failure.” Nature Reviews Cardiology 19, no. 6 (2022): 364–78. https://doi.org/10.1038/s41569-022-00692-y. % review, mechanical modulation of microtubules proposed as potential therapeutic target in heart failure

% %%% Microtubule networks

% %%% Tubulin structures
% \bibitem[]{}
% Alushin, Gregory M., Gabriel C. Lander, Elizabeth H. Kellogg, Rui Zhang, David Baker, and Eva Nogales. “High-Resolution Microtubule Structures Reveal the Structural Transitions in Αβ-Tubulin upon GTP Hydrolysis.” Cell 157, no. 5 (2014): 1117–29. https://doi.org/10.1016/j.cell.2014.03.053. % primary, structure and conformational changes with taxol binding and GTP hydrolysis

% %%% Existing measurements
% \bibitem[]{}
% Mameren, Joost van, Karen C. Vermeulen, Fred Gittes, and Christoph F. Schmidt. “Leveraging Single Protein Polymers To Measure Flexural Rigidity.” The Journal of Physical Chemistry B 113, no. 12 (2009): 3837–44. https://doi.org/10.1021/jp808328a. % primary, optical trapping

% %%% Existing models

% %%% Microtubule bundles
% \bibitem[]{}
% Soheilypour, Mohammad, Mohaddeseh Peyro, Stephen J. Peter, and Mohammad R.K. Mofrad. “Buckling Behavior of Individual and Bundled Microtubules.” Biophysical Journal 108, no. 7 (2015): 1718–26. https://doi.org/10.1016/j.bpj.2015.01.030. % primary

% %%% Microtubules in cells
% \bibitem[]{}
% Brangwynne, Clifford P., Frederick C. MacKintosh, Sanjay Kumar, et al. “Microtubules Can Bear Enhanced Compressive Loads in Living Cells Because of Lateral Reinforcement.” Journal of Cell Biology 173, no. 5 (2006): 733–41. https://doi.org/10.1083/jcb.200601060. % primary
% \bibitem[]{}
% Li, Teng. “A Mechanics Model of Microtubule Buckling in Living Cells.” Journal of Biomechanics 41, no. 8 (2008): 1722–29. https://doi.org/10.1016/j.jbiomech.2008.03.003. % primary

% %%% Other
% \bibitem[Okenve-Ramos et al, 2024]{neur_aging}
% Okenve-Ramos, Pilar, Rory Gosling, Monika Chojnowska-Monga, et al. “Neuronal Ageing Is Promoted by the Decay of the Microtubule Cytoskeleton.” PLOS Biology 22, no. 3 (2024): e3002504. https://doi.org/10.1371/journal.pbio.3002504. 
% \bibitem[]{}
% Needleman, Daniel J., Miguel A. Ojeda-Lopez, Uri Raviv, et al. “Synchrotron X-Ray Diffraction Study of Microtubules Buckling and Bundling under Osmotic Stress: A Probe of Interprotofilament Interactions.” Physical Review Letters 93, no. 19 (2004): 198104. https://doi.org/10.1103/PhysRevLett.93.198104. % primary, shape change with osmotic stress and looking at interprotofilament bond strengths
% \bibitem[]{}
% Mickey, B., and J. Howard. “Rigidity of Microtubules Is Increased by Stabilizing Agents.” The Journal of Cell Biology 130, no. 4 (1995): 909–17. https://doi.org/10.1083/jcb.130.4.909.

% % 
%     \item Some experiments have noted bending behaviors that would deviate from elastic behavior, including length-dependent elastic modulus [] and increased deformation with repeated bending []. There are currently multiple possible explanations for these deviations from elastic behavior, including isotropic assumptions in modeling [] or microtubule damage []. (also bending past thin beam model?)

%     %    
%     While the viscoelastic characteristics of cross-linked microtubule networks are established [multiple], similar investigations have not been performed for single microtubules.
%     \item The most challenging barrier in making such measurements is...? The high stiffness of microtubules makes these measurements more challenging than for other cytoskeletal filaments [], where time-dependent mechanical properties have also been established []. Is this true, check on that. Perhaps see if need to be characterized by more than a single number? What is the challenge then? Because some papers HAVE done stuff like that perhaps. But at least address the other changes? Memet and low/high strain regimes differences and their measurements, they have a model as well...so take another look at how what you're proposing actually addresses a gap or not, and if it doesn't, see what further steps you can take that would be VE/SM relevant! Go through that paper and see what some next steps might be. READ THROUGH MEMET AND CHECK THAT THEN ALSO SEE WHAT COULD GO A BIT FURTHER!!