\documentclass[preprint,12pt,authoryear]{elsarticle}
\input{instr-preamble}
\input{instr-mathsymbols}
\journal{ME517---Mechanics of Soft Materials}
\setlength{\marginparwidth}{2cm}
\newcommand\C[1]\null %\C{for inline comments}
\begin{document}

% \include{instr-part1}
\section{Statement of Research Interest}
Microtubules are a core component of the cellular cytoskeleton, a network of filaments in cells that contribute to varied mechanical processes including shape maintenance, force generation, and motility. Microtubule networks are generally acknowledged as displaying viscoelastic behavior, attributed to the collective behavior of the network [\cite{visco_review, visco_MTs}]. Other cytoskeletal filaments (including actin and intermediate filaments) are also well-known as being viscoelastic. However, the individual microtubules themselves are commonly treated as elastic due to their high stiffness relative to other cytoskeletal filaments. Yet, there are some behaviors of individual microtubules (notably, for certain types and compositions of microtubules) that cannot be explained by a purely elastic model. Single microtubules show increased deformation over time with repeated bending by the same hydrodynamic force, as well as a length-dependent persistence length [\cite{acetyl_aging, Celeg_lumen}]. Therefore, I propose a project exploring the potential viscoelastic properties of individual microtubules. In this project, I would first characterize the (potential) viscoelastic properties of microtubules using active bending experiments in an optical trap. Then, I would explore the mechanisms by which the viscoelastic properties of microtubules arise---or, in the case that microtubules do not generally show viscoelastic properties, the mechanisms by which some microtubules demonstrate certain viscoelastic properties like relaxation.

I am interested in studying this topic for two main reasons. First, I am very interested in mechanobiology as a field and want to better understand the mechanical properties of biological systems. Second, I want to bring a stronger physical and mechanical perspective to my current research on microtubule mechanics. There are a lot of papers noting how the mechanical properties of microtubules are more complex than a simple homogeneous rod, so I want to push this idea a little further by actually applying it to experiments. Hopefully, doing so will allow a better understanding of how microtubules respond to and generate forces in cells, as well as how their molecular composition (for example, microtubules are made of thinner protofilaments which have lateral interactions of a different strength than the longitudinal interactions that build the protofilaments) ends up resulting in their mechanical properties.


% bring this physical and mechanical perspective to my current research with microtubules.

% I am interested in studying the viscoelastic properties of individual microtubules for a couple of reasons. First of all, I am really interested in mechanobiology and how biological systems have adapted to work around or use physical forces. I am currently in a microtubule-focused lab that is well-equipped to study how different microtubule vary in their properties (based on different compositions or biochemical modifications). The lab also does research on kinesin motors and does have the ability to do whole cell (which could add to microtubule network studies) experiments as well. I want to bring my mechanical interests and physics background into my research more strongly. Plus, the lab has an optical trap that is well-suited to single molecule (or network) studies of microtubules, which I'm hoping to use to help bring a more mechanical and soft materials perspective to my research.

% Microtubules are a core component of the cellular cytoskeleton, a network of intracellular filaments that participate in or contribute to various mechanical processes including shape maintenance, force generation, and cell motility. Microtubule networks are acknowledged as having viscoelastic behavior, generally attributed to being an emergent property from the collective behavior of the network [\cite{visco_review, visco_MTs}]. As the stiffest of the cytoskeletal filaments, microtubule deformation is commonly treated as that of a stiff, elastic rod (citation). However, some microtubules also demonstrate behaviors inconsistent with a purely elastic filament, and which indicate that individual microtubules might also exhibit viscoelastic behaviors. For example, after repeated bending through hydrodynamic flow, certain varieties of microtubules will demonstrate increased bending deformation under the same applied flow force and therefore show relaxation upon repeated force application [\cite{acetyl_aging}]. In addition, some microtubules show a length-dependence in measured persistence length, an idea inconsistent with the buckling of an isotropic elastic rod [\cite{Celeg_lumen}]. Therefore, I would like to explore the viscoelastic properties of individual microtubules, first characterizing these properties and then exploring the mechanisms by which these viscoelastic properties arise for certain microtubule varieties. This would be done by optical trapping (like bending microtubules, condense and fit this in more clearly).

\section{Intellectual Merit}
Microtubules and their mechanical properties are addressed across many experimental and computational papers. However, there is both a wide range of experimentally measured values for microtubule stiffness and a limited understanding of how microtubules establish their mechanical properties. This is an especially interesting question because recent papers have noted that microtubules of different chemical compositions display different mechanical properties [\cite{Celeg_lumen}]. Determining whether individual microtubules display viscoelastic properties has the potential to address the current discrepancies between mechanical measurements focused on finding a single elastic modulus by more wholistically describing the mechanical properties of microtubules. Even if individual microtubules are not viscoelastic (which is absolutely possible!), establishing this concretely will allow further investigation of the select viscoelastic properties microtubules \emph{do} display. Regardless of the results, a better understanding of how individual microtubules behave in response to different mechanical stimuli (such as varied loading rates, repeated loading, or deformation directions) will develop our understanding of how microtubules actually deform in conditions where they do not form cross-linked networks (for example, filamentous bundles or single microtubules). 

In this course, lecture materials on viscoelastic bending and experimental techniques used to characterize the soft material properties of actual physical systems will be beneficial to this research proposal. Discussions of how to differentiate elastic from viscoelastic behavior and concerning the viscoelastic behaviors of thin filaments will be particularly applicable.


% At least based on my current understanding of mechanics, course materials on viscoelastic bending and experimental techniques used to characterize the soft material properties of a system will be related to (and help propose) this research idea.
%in contrast, actin filaments have a consistently charachterized bending stiffness/mechanical behaviors in response to forces; mechanical properties and behaviors; in different conditions (such as different microtubule lengths) 
% Microtubules and their mechanical properties have been the subject of numerous experiments and physical models (citations). However, there is a limited understanding of where microtubule mechanics come from and how they might vary under different circumstances. In particular, current mechanical measurements and models show highly conflicting results in measured bending stiffness and other mechanical properties. A better understanding of microtubule mechanics by investigating whether they act as viscoelastic systems could serve to resolve some of these conflicts by (explaining? addressing? providing a potential explanation or expansion on the current model?) expanding the current models of microtubule bending to include more complex behaviors. That is, characterizing the viscoelastic properties of individual microtubules will provide a more robust understanding of how microtubules behave mechanically--or the lack thereof will hint to another mechanism governing the uncertainty in how they behave mechanically. A better understanding of how microtubules behave mechanically in different conditions will also help understand how microtubules actually deform in cells under conditions where they do not form networks with crosslinking that would lead to emergent viscoelasticity. For example, understanding how microtubule bundles or other filamentous formations (more filamentous microtubule bundles rather than crosslinked mesh networks with known viscoelastic behavior responses) behave mechanically. And how they experience different forces and respond under different conditions in ways that could impact cell function and mechanics in different conditions. Also understand how microtubules age and change mechanically over time as they exist in cells and are subject to repeated bending (if not dynamic??) over time in the cell.

% Relaxation of bending? Definitely go back to the syllabus a bit more. different lens as well? emergent vs induvidual property at a broader scale? better understanding of MT mechanics to resolve conflicting measurements--made under different conditions? also better understanding of how MTs actually deform in cells in different conditions and that experience different forces--like how it could tell us whether we expect there to be other VE properties that could impact cell function, mechanics, etc.

\section{Broader Impact}
In many non-dividing cell types, microtubules are relatively long-lasting and therefore subject to repeated stressing and bending. Better understanding the mechanics of microtubules would contribute to understanding the functional roles of microtubules in such cell types. For example, cardiomyocytes are specialized cells important for the repeated contractions of the heart. In these cells, there are also microtubules that are both essential to these contractions and that have to endure repeated bending and straightening [\cite{cardmy_review}]. A better understanding of how microtubules deform in response to stress could allow us to better understand the mechanics of hear muscle contraction. In addition, understanding what mechanical of microtubules properties are necessary for proper heart function has the potential to be used in health applications, as the mechanical modulation of microtubules has been proposed as a potential therapeutic target in heart failure [\cite{card_HF}]. 

% In non-dividing cells, certain microtubules are subject to repeated stressing and bending. For example, cardiomyocytes are specialized heart cells important in contraction. In these cells, microtubules are also repeatedly bent and straightened from this repeated contraction [\cite{cardmy_review}]. With the stiffness of this microtubule network important to the proper function of the heart, a better understanding of how individual microtubules bend and more specifically how their bending properties change with this repeated deformation could contribute to a better understanding of their overall function in the heart [\cite{card_HF}]. In addition, deviations from expected relaxation behavior could point to new proteins responsible for maintaining proper microtubule flexibility with repeated bending.
% (this might be a stretch) In addition, neurons have long-lived microtubules that are part of transport (more on this). While these microtubules do not serve a primary role in (resisting?) mechanics, (time-dependent) changes in the microtubule material properties over time due to forces--whether external or from (on the smaller scale of, could test both force ranges) intracellular interactions with transport molecules or the crowded cytoplasm would be important in the resistance of the microtubules to breakage? Since 

% can help differentiate effects of the microtubule itself and proteins that help to offset bending with age like acetylation or MAPS

% While studies exist that investigate the roles of MAPs and crowding in stabilizing microtubules. how contributes to society like health applications vs better understanding of some phenomena folks are interested in understanding
% oh but more stiff is part of heart failure
% Better understanding of how microtubules age over time. Bundles of microtubules
% Potential for platelets and cardiomyocytes that have constantly bent (are these dynamic?) microtubules or repeated mechanical contractions respectively.


\begin{thebibliography}{00}

% using Chicago 18th shortened from Zotero
\bibitem[Corominas-Murtra and Petridou, 2021]{visco_review}
Corominas-Murtra, Bernat, and Nicoletta I. Petridou. “Viscoelastic Networks: Forming Cells and Tissues.” Frontiers in Physics 9 (2021). https://doi.org/10.3389/fphy.2021.666916.
\bibitem[Lin et al., 2007]{visco_MTs}
Lin, Yi-Chia, Gijsje H. Koenderink, Frederick C. MacKintosh, and David A. Weitz. “Viscoelastic Properties of Microtubule Networks.” Macromolecules 40, no. 21 (2007): 7714–20. https://doi.org/10.1021/ma070862l.
\bibitem[Portran et al., 2017]{acetyl_aging}
Portran, Didier, Laura Schaedel, Zhenjie Xu, Manuel Théry, and Maxence V. Nachury. “Tubulin Acetylation Protects Long-Lived Microtubules against Mechanical Ageing.” Nature Cell Biology 19, no. 4 (2017): 391–98. https://doi.org/10.1038/ncb3481.
\bibitem[Yucheng et al., 2025]{Celeg_lumen}
Ye, Yucheng, Zheng Hao, Jingyi Luo, et al. “Tubulin Isotypes of C. Elegans Harness the Mechanosensitivity of the Lattice for Microtubule Luminal Accessibility.” Nature Physics, ahead of print (2025). https://doi.org/10.1038/s41567-025-02983-w.
\bibitem[Uchida et al., 2022]{cardmy_review}
Uchida, Keita, Emily A. Scarborough, and Benjamin L. Prosser. “Cardiomyocyte Microtubules: Control of Mechanics, Transport, and Remodeling.” Annual Review of Physiology 84, no. Volume 84, 2022 (2022): 257–83. https://doi.org/10.1146/annurev-physiol-062421-040656.
\bibitem[Caporizzo and Prosser, 2022]{card_HF}
Caporizzo, Matthew A., and Benjamin L. Prosser. “The Microtubule Cytoskeleton in Cardiac Mechanics and Heart Failure.” Nature Reviews Cardiology 19, no. 6 (2022): 364–78. https://doi.org/10.1038/s41569-022-00692-y.
\bibitem[Okenve-Ramos et al, 2024]{neur_aging}
Okenve-Ramos, Pilar, Rory Gosling, Monika Chojnowska-Monga, et al. “Neuronal Ageing Is Promoted by the Decay of the Microtubule Cytoskeleton.” PLOS Biology 22, no. 3 (2024): e3002504. https://doi.org/10.1371/journal.pbio.3002504.

\bibliographystyle{elsarticle-harv} 
% \bibliography{cas-refs}
\end{thebibliography}

\include{Dawson-PS1}

\end{document}

% Section 1 Notes
% by which the VE properties of MTs are established microtubules vary in exhibiting these properties

%These results indicate that individual microtubules might also exhibit viscoelastic behaviors.
%as well as a decreased persistence length
%individual \C{deacetylated} microtubules showed an increase in deformation 

% importnat for understanding networks and deformations over time? where would a MT act more independently rather than in a bundle though, or why would the single molecule mechanical properties actually matter?
% However, recent papers have demonstrated that individual microtubules might exhibit viscoelastic behaviors

% Microtuuuuuuuubles.
% Looking at them from a viscoelastic perspective, particularly in terms of relaxation.
% Single microtubules, but could also do networks or bundles that have already been looked at as viscoelastic?